RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data

### 2015-04-19 paper/paper7/paper7.tex
content-driven constraint types

We determined the default \textbf{\emph{severity level}} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \textbf{\emph{sets of constraints}}:
\begin{enumerate}
	\item $\mathcal{SL}_{0}$: set of constraints with severity level \emph{informational}
	\item $\mathcal{SL}_{1}$: set of constraints with severity level \emph{warning}
	\item $\mathcal{SL}_{2}$: set of constraints with severity level \emph{error}
\end{enumerate}
Violations of $\mathcal{SL}_{0}$ constraints point to possible data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically or semantically not correctly represented.
The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that $\mathcal{SL}_{1}$ invalid data could be
whereas $\mathcal{SL}_{1}$ invalid data cannot be processed further. 
Although, we provide default severity levels for each constraint, users should be able to specify constraints' severity levels according to their individual needs, i.e., use case specific severity levels.

@@

\subsection{Content-Driven Constraint Types}
\label{content-driven-validation}
\ke{@KAI: Dieses Kapitel werde ich noch umorganisieren! Die einzelnen Paragraphen sollten zusammengehörigen Clustern von constraint types entsprechen!}

\tb{short description}

\textbf{Observations of Aggregated Data Sets.}
The purpose of some constraints is to ensure the integrity of
the data according to intended data model semantics (\emph{data model consistency}).
Every \emph{qb:Observation}, e.g., must have a value for each dimension
declared in its associated \emph{qb:DataStructureDefinition} ($\mathcal{SL}_{2}$)
and no two \emph{qb:Observations} in the same \emph{qb:DataSet}
may have the same value for all dimensions ($\mathcal{SL}_{1}$).
If a \emph{qb:DataSet} \emph{D} has a \emph{qb:Slice} \emph{S}, and \emph{S} has an
\emph{qb:Observation} \emph{O}, then the \emph{qb:DataSet} corresponding to \emph{O} must be \emph{D} ($\mathcal{SL}_{1}$).

%- for each dimension there should be a description and code lists.
%
%- for each code list there should be a description.
%
%- there should be a relationship to the underlying person-level data.

\textbf{Series, Studies, Data Sets, and Data Files.}
It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
To get an overview over a series/study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
If an abstract and an external description are absent, 
a title or an alternative title has to be stated ($\mathcal{SL}_{1}$).
For datatype properties it should be possible to declare frequently needed \emph{facets} ({\emph{R-46}) to drive user interfaces and validate input against simple conditions including min/max values, regular expressions, and string length.
The abstract of series/studies, e.g., should have a minimum length (\emph{xsd:minLength}; $\mathcal{SL}_{1}$).
\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals of certain types.
If a study, e.g., has no associated data sets ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
If there is no metadata on data files including the actual data of data sets (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the underlying study is not sufficient.
The case quantity measures how many cases are collected for a study.
A high case and variable quantity is an indicator for high statistical quality and comprehensiveness of the conducted study ($\mathcal{SL}_{1}$).

\textbf{Variables and Variable Comparison.}
Each variable should have a variable representation (\emph{R-86}; $\mathcal{SL}_{1}$), which is either an (un)ordered code list or a union of datatypes.
In case of a code list, associated categories (human-readable labels) may be stated (\emph{R-71}; $\mathcal{SL}_{0}$).
The variable \emph{Education at pre-school} is represented as ordered code list without any categories.
If a {\em skos:Concept} stands for a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}) (\emph{R-71}; $\mathcal{SL}_{2}$).
Variables may have at least one relationship to a theoretical concept ({\emph{R-86}; $\mathcal{SL}_{0}$).
%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
The default severity level of this constraint is weak, as in most cases research can be continued without associated theoretical concepts.
A very common research question is to compare variables of multiple studies or countries (\emph{comparison}).
To compare variables, 
(1) variables and (2) variable definitions must be present,
(3) code lists must be structured properly,
(4) for each code an associated category (human-readable label) must be specified, and
(5) code lists must either be identical or at least similar.
If a researcher wants to get a first overview over comparable variables (use case 1), 
covering the first three constraints may be sufficient for this purpose.
Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than the severity level of the next two constraints ($\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$).
If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining two constraints is getting more serious.

\textbf{Descriptive Statistics.}
The property \emph{disco:percentage} stands for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set.
Percentage values are only valid when they are within the \emph{literal range} of 0 and 100 (\emph{R-45}; $\mathcal{SL}_{2}$).
{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
The sum of percentage values of all codes of a variable code list, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
and the minimum of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
Codes (\emph{skos:Concept}) are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within variable representations.
In order to check the correctness of relative frequencies' calculations, the cumulative percentage (\emph{disco:cumulativePercentage}) of the current code must exactly be the cumulative percentage of the previous code
plus the percentage value (\emph{disco:percentage}) of the current code (\emph{data model consistency}; $\mathcal{SL}_{2}$).

\textbf{Unique Identification.}
It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data. 
In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
which is therefore inverse-functional
$(\ms{funct identifier}\sp{\overline{\ }})$,
i.e. for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} ($\mathcal{SL}_{2}$).
Keys, however, are even more general than inverse-functional properties (\emph{R-58}),
as a key can be a data, an object property, or a chain of properties \cite{Schneider2009}.
For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
DL is extended with \emph{key boxes} and a special \emph{keyfor} construct (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005}.
OWL 2 \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
%OWL 2 hasKey can be used to identify resources uniquely
%
%We used Protégé 5.
%
%example: owl:Thing owl:hasKey ( :hasSSN ) . :Peter :hasSSN "123-45-6789" .
%:Peter_Griffin :hasSSN "123-45-6789" .
%
%We use the predefined Reasoner HermiT.
%
%:Peter and :Peter_Griffin are derived as identical from the reasoner as they have the same value for :hasSSN.
%
%hasKey can be used to merge resources and to recognize constraint violations.
%
%Alternative to OWL 2 hasKey: concise bounded description (proposal of Dan)
%
%action: explore CBD document solution might be using both approaches
%
%benefit: additional identification to URI / IRI benefit: compound properties can be used as key

\textbf{Membership in Controlled Vocabularies.}
In many cases, resources must be members of controlled vocabularies (\emph{R-32}).
If a dimension property, e.g., has a \emph{qb:codeList},
then the value of the dimension property on every \emph{qb:Observation} must be in the code list ($\mathcal{SL}_{2}$).
Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
Summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).

%\begin{center}
%\begin{DL}
%SummaryStatistics $\sqsubseteq$ $\forall summaryStatisticType.A$ \\
%$A \equiv Concept \sqcap \forall inScheme . B$ \\
%$B \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
%\end{DL}
%\end{center}

\textbf{Coverage.}
Information about the temporal (\emph{dcterms:temporal}), the spatial (\emph{dcterms:spatial}), and the topical coverage (\emph{dcterms:subject}) of series, studies, data sets, and data files (\emph{R-86}; $\mathcal{SL}_{1}$) is of interest when performing frequently formulated queries 
	(e.g. to search for all data sets of given years (temporal coverage) in which data is collected in certain countries (spatial coverage) about particular topics (topical coverage)).
Depending on property datatypes,
two different literal values have
a specific ordering with respect to an operator like \textless (\emph{R-43: literal value comparison}).
Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}) ($\mathcal{SL}_{2}$).

%\textbf{Organizations, Hierarchies, Classifications, and Ordering.}
\textbf{Hierarchies and Ordering.}
SKOS is based on RDF, which is a graph-based data model. Therefore, we can concentrate on the vocabulary's graph-based structure for assessing the quality of SKOS vocabularies and apply graph- and network-analysis techniques (\emph{structure}) like 
(1) a vocabulary should provide entry points (top concepts) to the data to provide efficient access and guidance for human users,
(2) concepts, internal to the tree, should not be indicated as top concepts, and
(3) a vocabulary should not contain many orphan concepts 
(concepts without any associative or hierarchical relations) lacking valuable context information. A controlled vocabulary that contains many orphan concepts is less usable for search and retrieval use cases.
%, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}. 
Objects and literals can be \emph{ordered} (\emph{R-121, R-217}) for given properties.
\emph{Disco }variables, questions, and codes/categories are typically organized in a particular order. 
If a variable code list should be ordered, the variable representation should be of the type \emph{skos:OrderedCollection} containing multiple codes/categories (each represented as \emph{skos:Concept}) in a \emph{skos:memberList}.

\textbf{Reusability.}
Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).
The constraint type \emph{context-specific exclusive or of property groups} (\emph{R-11})
restricts individuals of given classes to have exactly one of multiple property groups.

@@

Constraints of some constraint types are directly and automatically derived from syntax and semantics of vocabularies' conceptual models.
As these constraints depend on data models' intended semantics, associated default severity levels are in most cases very strong ($\mathcal{SL}_{2}$).

\textbf{Cardinality Restrictions.}
An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
A \emph{phdd:TableStructure}, e.g., has at least one \emph{phdd:column} relationship to a \emph{phdd:Column} (\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}),
a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}), and a \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).

\textbf{Language Tag Cardinality.}
For data properties, it may be desirable to restrict that values of predefined languages must be present for determined number of times (\emph{R-48, R-49}):
(1) Some controlled vocabularies contain literals in natural language, but without information what language has actually been used. 
(2) Language tags must conform to language standards. 
(3) Some thesaurus concepts are labeled in only one, others in multiple languages. It may be desirable to have each concept labeled in each of the languages that are also used on the other concepts. Although not always possible, incompleteness of language coverage for some concepts may indicate shortcomings of thesauri
\cite{MaderHaslhoferIsaac2012}.

>>>>

We determined the default \textbf{\emph{severity level}} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \textbf{\emph{sets of constraints}}:
\begin{itemize}
	\item $\mathcal{SL}_{0}$: set of constraints with severity level \emph{informational}
	\item $\mathcal{SL}_{1}$: set of constraints with severity level \emph{warning}
	\item $\mathcal{SL}_{2}$: set of constraints with severity level \emph{error}
\end{itemize}
Violations of $\mathcal{SL}_{0}$ constraints point to possible data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically or semantically not correctly represented.
The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that $\mathcal{SL}_{1}$ invalid data could be
whereas $\mathcal{SL}_{1}$ invalid data cannot be processed further. 
Although, we provide default severity levels for each constraint, users should be able to specify constraints' severity levels according to their individual needs, i.e., use case specific severity levels.

@@

$\mathcal{CT}_{T}$ constraints can be directly and automatically derived from explicitly stated syntax and semantics of vocabularies' data models.
Thus, associated default severity levels are in most cases very strong ($\mathcal{SL}_{2}$).

\textbf{Existential Quantifications.}
\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals of certain types.
If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
Case quantity measures how many cases are collected for a study.
High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
Variables should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
The variable \emph{Education at pre-school},.e.g, is associated with the theoretical concept \emph{Child Care}. 
The constraint's severity level is weak, as in most cases research can be continued without having information about theoretical concepts.

\textbf{Cardinality Restrictions on Properties and Language Tags.}
%An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
%Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
A \emph{phdd:TableStructure}, e.g., has at least one \emph{phdd:column} relationship to a \emph{phdd:Column} (\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}),
a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}), and a \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).

%\textbf{Language Tag Cardinality.}
For data properties, it may be desirable to restrict that values of predefined languages must be present for determined number of times (\emph{R-48, R-49}):
(1) Some controlled vocabularies contain literals in natural language, but without information what language has actually been used. 
(2) Language tags must conform to language standards. 
(3) Some thesaurus concepts are labeled in only one, others in multiple languages. It may be desirable to have each concept labeled in each of the languages that are also used on the other concepts. Although not always possible, incompleteness of language coverage for some concepts may indicate shortcomings of thesauri
\cite{MaderHaslhoferIsaac2012}.

\subsection{Content-Driven Constraint Types}
\label{content-driven-validation}

In this sub-chapter, we assign default severity levels to and describe constraints of diverse $\mathcal{CT}_{C}$ constraint types 
to ensure that the data is consistent with the intended syntax, semantics, and integrity of vocabularies' data models.

%\textbf{Observations of Aggregated Data Sets.}
%- for each dimension there should be a description and code lists.
%- for each code list there should be a description.
%- there should be a relationship to the underlying person-level data.

\textbf{Data Model Consistency.}
The purpose of some constraints is to ensure the integrity of
the data according to intended data model semantics (\emph{data model consistency}).
Every \emph{qb:Observation}, e.g., must have a value for each dimension
declared in its \emph{qb:DataStructureDefinition} ($\mathcal{SL}_{2}$)
and no two \emph{qb:Observations} in the same \emph{qb:DataSet}
can have the same value for all dimensions ($\mathcal{SL}_{1}$).
If a \emph{qb:DataSet} \emph{D} has a \emph{qb:Slice} \emph{S}, and \emph{S} has an
\emph{qb:Observation} \emph{O}, then the \emph{qb:DataSet} corresponding to \emph{O} must be \emph{D} ($\mathcal{SL}_{1}$).
Relative frequencies of variable codes are calculated correctly, if the cumulative percentage (\emph{disco:cumulativePercentage}) of a given code exactly matches the cumulative percentage of the previous code
plus the percentage value (\emph{disco:percentage}) of the current code ($\mathcal{SL}_{2}$).

%\textbf{Hierarchies and Ordering.}
\textbf{Structure and Ordering.}
For assessing the quality of \emph{SKOS} vocabularies, we concentrate on graph-based structures and apply graph- and network-analysis techniques (\emph{structure}) like 
(1) a thesaurus should provide entry points (top concepts) to the data to provide efficient access and guidance for human users,
(2) concepts, internal to the tree, should not be indicated as top concepts, and
(3) a thesaurus should not contain many orphan concepts 
(concepts without any associative or hierarchical relations) lacking valuable context information for retrieval.
%, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}. 
Objects/literals can be declared to be \emph{ordered} (\emph{R-121, R-217}) for given properties.
Variables, questions, and codes, e.g., are typically organized in a particular order. 
If codes (\emph{skos:Concept}) should be ordered, they must be members (\emph{skos:memberList}) in an ordered collection (\emph{skos:OrderedCollection}), the variable's code list.

\textbf{Comparison.}
A very common research question is to compare variables of multiple studies or countries (\emph{comparison}).
To compare variables, 
(1) variables and (2) variable definitions must be present,
(3) code lists must be structured properly,
(4) for each code an associated category must be specified, and
(5) code lists must either be identical or at least similar.
If a researcher wants to get a first overview over comparable variables (use case 1), 
covering the first three constraints may be sufficient.
Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than for the last two constraints ($\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$).
If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining two constraints is getting more serious.

\textbf{Unique Identification.}
It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data. 
In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
which is therefore inverse-functional
$(\ms{funct identifier}\sp{\overline{\ }})$,
i.e. for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} ($\mathcal{SL}_{2}$).
Keys, however, are even more general than \emph{inverse-functional properties} (\emph{R-58}),
as a key can be a data, an object property, or a chain of properties \cite{Schneider2009}.
For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
DL is extended with \emph{key boxes} and the construct \emph{keyfor} (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005}.
OWL 2 \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.

\textbf{Membership in Controlled Vocabularies.}
In many cases, resources must be \emph{members of controlled vocabularies} (\emph{R-32}).
If a dimension property, e.g., has a \emph{qb:codeList},
then the value of the dimension property on every \emph{qb:Observation} must be in the code list ($\mathcal{SL}_{2}$).
Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
Thus, summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).

\textbf{Constraints on Properties.}
It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
To get an overview over a series/study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
If an abstract and an external description are absent, however,  
a title or an alternative title should be given ($\mathcal{SL}_{1}$).
In case a variable is represented in form of a code list, codes may be associated with categories, i.e., human-readable labels ($\mathcal{SL}_{0}$).
The variable \emph{Education at pre-school}, e.g., is represented as ordered code list without any categories.
If a {\em skos:Concept} represents a code (having {\em skos:notation} and {\em skos:prefLabel} properties), 
then the property {\em disco:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases ($\mathcal{SL}_{2}$).
Constraints of type \emph{context-specific exclusive or of property groups} (\emph{R-11})
restrict individuals of given classes to have properties defined within exactly one of multiple property groups.
\emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).
For datatype properties, it should be possible to declare frequently needed \emph{facets} ({\emph{R-46}) to validate input against simple conditions including min/max values, regular expressions, and string length.
The abstract of series/studies, e.g., should have a minimum length ($\mathcal{SL}_{1}$).

\textbf{Constraints on Literals.}
\emph{disco:percentage} stands for the number of cases of a given code in relation to the total number of cases for a particular variable.
Percentage values are only valid when they are within the \emph{literal range} of 0 and 100 (\emph{R-45}; $\mathcal{SL}_{2}$).
{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
The sum of percentage values of all variable codes, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
and the minimum absolute frequency of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
Depending on property datatypes, two different literal values have
a specific ordering with respect to an operator like \textless (\emph{R-43: literal value comparison}).
Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}) ($\mathcal{SL}_{2}$).

@@

%\textbf{Series, Studies, Data Sets, and Data Files.}
%It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
%To get an overview over a series/study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
%If an abstract and an external description are absent, however,  
%a title or an alternative title should be given ($\mathcal{SL}_{1}$).
%For datatype properties, it should be possible to declare frequently needed \emph{facets} ({\emph{R-46}) to validate input against simple conditions including min/max values, regular expressions, and string length.
%The abstract of series/studies, e.g., should have a minimum length ($\mathcal{SL}_{1}$).
%\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals of certain types.
%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
%Case quantity measures how many cases are collected for a study.
%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
%
%\textbf{Variables and Variable Comparison.}
%Variables should be represented (\emph{R-86}; $\mathcal{SL}_{1}$) either as (un)ordered code lists or as unions of datatypes.
%In case of a code list, associated categories (human-readable labels) may be stated (\emph{R-71}; $\mathcal{SL}_{0}$).
%The variable \emph{Education at pre-school}, e.g., is represented as ordered code list without any categories.
%If a {\em skos:Concept} represents a code (having {\em skos:notation} and {\em skos:prefLabel} properties), 
%then the property {\em disco:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases (\emph{R-71}; $\mathcal{SL}_{2}$).
%Variables may have at least one relationship to a theoretical concept ({\emph{R-86}; $\mathcal{SL}_{0}$).
%%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
%The variable \emph{Education at pre-school},.e.g, is associated with the theoretical concept \emph{Child Care}. 
%The default severity level of this constraint is weak, as in most cases research can be continued without associated theoretical concepts.
%A very common research question is to compare variables of multiple studies or countries (\emph{comparison}).
%To compare variables, 
%(1) variables and (2) variable definitions must be present,
%(3) code lists must be structured properly,
%(4) for each code an associated category (human-readable label) must be specified, and
%(5) code lists must either be identical or at least similar.
%If a researcher wants to get a first overview over comparable variables (use case 1), 
%covering the first three constraints may be sufficient for this purpose.
%Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than the severity level of the next two constraints ($\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$).
%If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining two constraints is getting more serious.
%
%\textbf{Descriptive Statistics.}
%The property \emph{disco:percentage} stands for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set.
%Percentage values are only valid when they are within the \emph{literal range} of 0 and 100 (\emph{R-45}; $\mathcal{SL}_{2}$).
%{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
%The sum of percentage values of all codes of a variable code list, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
%and the minimum of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
%Codes (\emph{skos:Concept}) are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within variable representations.
%In order to check the correctness of relative frequencies' calculations, the cumulative percentage (\emph{disco:cumulativePercentage}) of the current code must exactly be the cumulative percentage of the previous code
%plus the percentage value (\emph{disco:percentage}) of the current code (\emph{data model consistency}; $\mathcal{SL}_{2}$).
%
%\textbf{Unique Identification.}
%It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data. 
%In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
%which is therefore inverse-functional
%$(\ms{funct identifier}\sp{\overline{\ }})$,
%i.e. for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} ($\mathcal{SL}_{2}$).
%Keys, however, are even more general than inverse-functional properties (\emph{R-58}),
%as a key can be a data, an object property, or a chain of properties \cite{Schneider2009}.
%For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
%DL is extended with \emph{key boxes} and a special \emph{keyfor} construct (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005}.
%OWL 2 \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
%%OWL 2 hasKey can be used to identify resources uniquely
%%
%%We used Protégé 5.
%%
%%example: owl:Thing owl:hasKey ( :hasSSN ) . :Peter :hasSSN "123-45-6789" .
%%:Peter_Griffin :hasSSN "123-45-6789" .
%%
%%We use the predefined Reasoner HermiT.
%%
%%:Peter and :Peter_Griffin are derived as identical from the reasoner as they have the same value for :hasSSN.
%%
%%hasKey can be used to merge resources and to recognize constraint violations.
%%
%%Alternative to OWL 2 hasKey: concise bounded description (proposal of Dan)
%%
%%action: explore CBD document solution might be using both approaches
%%
%%benefit: additional identification to URI / IRI benefit: compound properties can be used as key
%
%
%\textbf{Membership in Controlled Vocabularies.}
%In many cases, resources must be members of controlled vocabularies (\emph{R-32}).
%If a dimension property, e.g., has a \emph{qb:codeList},
%then the value of the dimension property on every \emph{qb:Observation} must be in the code list ($\mathcal{SL}_{2}$).
%Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
%Summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
%
%%\begin{center}
%%\begin{DL}
%%SummaryStatistics $\sqsubseteq$ $\forall summaryStatisticType.A$ \\
%%$A \equiv Concept \sqcap \forall inScheme . B$ \\
%%$B \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
%%\end{DL}
%%\end{center}
%
%\textbf{Coverage.}
%Information about the temporal (\emph{dcterms:temporal}), the spatial (\emph{dcterms:spatial}), and the topical coverage (\emph{dcterms:subject}) of series, studies, data sets, and data files (\emph{R-86}; $\mathcal{SL}_{1}$) is of interest when performing frequently formulated queries 
	%(e.g. to search for all data sets of given years (temporal coverage) in which data is collected in certain countries (spatial coverage) about particular topics (topical coverage)).
%Depending on property datatypes,
%two different literal values have
%a specific ordering with respect to an operator like \textless (\emph{R-43: literal value comparison}).
%Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}) ($\mathcal{SL}_{2}$).
%
%%\textbf{Organizations, Hierarchies, Classifications, and Ordering.}
%\textbf{Hierarchies and Ordering.}
%SKOS is based on RDF, which is a graph-based data model. Therefore, we can concentrate on the vocabulary's graph-based structure for assessing the quality of SKOS vocabularies and apply graph- and network-analysis techniques (\emph{structure}) like 
%(1) a vocabulary should provide entry points (top concepts) to the data to provide efficient access and guidance for human users,
%(2) concepts, internal to the tree, should not be indicated as top concepts, and
%(3) a vocabulary should not contain many orphan concepts 
%(concepts without any associative or hierarchical relations) lacking valuable context information. A controlled vocabulary that contains many orphan concepts is less usable for search and retrieval use cases.
%%, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}. 
%Objects and literals can be \emph{ordered} (\emph{R-121, R-217}) for given properties.
%\emph{Disco }variables, questions, and codes/categories are typically organized in a particular order. 
%If a variable code list should be ordered, the variable representation should be of the type \emph{skos:OrderedCollection} containing multiple codes/categories (each represented as \emph{skos:Concept}) in a \emph{skos:memberList}. 
%
%\textbf{Reusability.}
%Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).
%The constraint type \emph{context-specific exclusive or of property groups} (\emph{R-11})
%restricts individuals of given classes to have exactly one of multiple property groups.
